---
title: "IF97"
format: html
---

```{r}
library()

# Warning in install.packages :
#   package ‘if97’ is not available for this version of R

# A version of this package for your version of R might be available elsewhere,
# see the ideas at
# https://cran.r-project.org/doc/manuals/r-patched/R-admin.html#Installing-packages


```


## if97: IAPWS-IF97 Equations for Regions 1, 2, 3 and 5

**CRAN**  

https://rdrr.io/cran/iapws/man/if97.html

**Description**  

Compute thermodynamic and transport properties of water and steam using the IAPWS industrial formulation 1997.

**Usage**  

if97(what, p, t, h, state = NULL)  

**Author(s)**

Jonathan Debove

**References**

1. International Association for the Properties of Water and Steam, IAPWS R7-97(2012), Revised Release on the IAPWS Industrial Formulation 1997 for the Thermodynamic Properties of Water and Steam.

2. International Association for the Properties of Water and Steam, IAPWS R12-08(2008), Release on the IAPWS Formulation 2008 for the Viscosity of Ordinary Water Substance.

3. International Association for the Properties of Water and Steam, IAPWS R15-11(2011), Release on the IAPWS Formulation 2011 for the Thermal Conductivity of Ordinary Water Substance.


## Example

```{r}
1 + 1
```

You can add options to executable code like this 

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
